\section{A Definition of ``Knowledge Graph''}

One thing to note is that the knowledge graph platforms that have been reviewed in this paper do not strictly adhere to the definition of knowledge graph that was set out in Stokman and de Vries \cite{Stokman_1988}, and Zhang \cite{zhang2002knowledge}.
Since usage has evolved it is appropriate to develop a definition that follows how the term is currently used.
Implicit in the name ``knowledge graph'' is, of course, that a knowledge graph represent \emph{knowledge}, and do so using a \emph{graph} structure.
Stokman,  de Vries \cite{Stokman_1988}, and Zhang \cite{zhang2002knowledge} posit useful definitions and requirements for knowledge graphs as a starting point:

\begin {itemize}
\item Knowledge graph meaning is expressed as structure.
\item Knowledge graph statements are unambiguous.
\item Knowledge graphs use a limited set of relation types.
\end {itemize}

In order for knowledge graphs statements to be unambiguous, they need to be composed of unambiguous units. 
\begin {itemize}
\item All identified entities in a knowledge graph, including types and relations, must be identified using global identifiers with unambiguous denotation.
\end {itemize}
One example of this kind of identifier is the Uniform Resource Identifier (URI) as used in the Resource Description Framework (RDF) \cite{cyganiak2014rdf}.
While the use of ``limited set of relation types'' addressed a specific set of non-decomposable relations above, in the context of an open world knowledge system this should be taken to mean a core set of relations and classes that subsume or can be used to compose any other key relations and classes.   
%deborah modified slightly above
This seems to be the case generally, as the reviewed knowledge graphs all attempt to build from a common vocabulary.

In practice, the knowledge graph literature and the practical knowledge graphs we reviewed either aggregate knowledge from many secondary sources and use Natural Language Processing (NLP) extraction when the sources are unstructured text, or use a semantic Extraction Transformation, and Load (ETL) process from structured databases \cite{McCusker_2009}.
Some knowledge graphs rely on crowdsourcing of their information (including the Google Knowledge Graph), a form of distributed curation.
At no point do we see a case where the knowledge does not have a theoretical, citeable source or some other recorded justification.
Since knowledge graphs nominally represent knowledge, we argue that some criteria for inclusion of content and its provenance should be encoded in the graph.
This is especially true for knowledge graphs gathered from other sources, as the sources themselves must have some justification for publishing their assertions.
\begin {itemize}
\item Knowledge graphs must include explicit provenance.
\end {itemize}
In many cases, the justification for inclusion of assertions appeals to authority, through the citation of the resource the knowledge was extracted from.
Authority, at least in scientific research, is only a short cut for validating knowledge, and good knowledge graphs should encode as much justification for their assertions as they can.
We consider graphs without provenance concerning attribution or justification to be ``bare statement'' graphs and not true knowledge graphs, since they provide no way to confirm that a given assertion can be justified or is even believed by the original asserter, which is a minimal (but not sufficient \cite{Gettier_1963}) criteria for ``knowledge'' in a knowledge graph.

\begin {itemize}
\item Knowledge graphs may include uncertainty assessments.
\end {itemize}

Some knowledge graphs go further in modeling knowledge by providing uncertainty assessments of the knowledge asserted \cite{Dong_2014}.
This can be useful when dealing with scientific knowledge graphs, where competing hypotheses and theories are known to be true to certain degrees, which may change as new evidence comes to light.
\begin {itemize}
\item Knowledge graphs embody knowledge that remains true.
\end {itemize}

This final requirement is rooted in the notion that knowledge should be ``timeless''.
Rospocher, \textit{et al.} define knowledge graphs as collections of time-invariant facts about entities \cite{Rospocher2016}.
More generally, a knowledge graph should focus on knowledge that remains true.
How best to represent this is up to the knowledge graph.